### 2020-08-27 README.Rmd
working through changes to readme with new package functions

```{r}
library(tidyverse)
library(forestecology)
library(snakecase)
library(skimr)
library(sf)
library(sfheaders)
# devtools::install_github("rvalavi/blockCV")
library(blockCV)
library(tictoc)
library(yardstick)
library(viridis)

@@

```{r, eval = run_scbi}
# SCBI
scbi_2013 <- 
  "https://github.com/SCBI-ForestGEO/SCBI-ForestGEO-Data/raw/master/tree_main_census/data/census-csv-files/scbi.stem2.csv" %>% 
  read_csv() %>% 
  select(
    treeID, stemID, sp, quadrat, gx, gy, dbh, 
    date = ExactDate, codes, status
  )

scbi_2018 <-
  "https://github.com/SCBI-ForestGEO/SCBI-ForestGEO-Data/raw/master/tree_main_census/data/census-csv-files/scbi.stem3.csv" %>% 
  read_csv() %>% 
  select(
    treeID, stemID, sp, quadrat, gx, gy, dbh, 
    date = ExactDate, codes, status
  ) %>% 
  mutate(dbh = as.numeric(dbh))
```

@@

bw_growth_df <-
  # Merge both censuses and compute growth:
  compute_growth(bw_census_2008, bw_census_2014, id) %>%
  mutate(sp = to_any_case(sp)) %>%
  # Convert data frame to sf object
  st_as_sf(coords = c("gx", "gy")) %>%
  # drop stemID
  select(-stemID)

@@

scbi_growth_df <- 
  # Merge both censuses and compute growth:
  compute_growth(census_df1, census_df2, id) %>%
  # they are mesuaring in mm while we are measuring in cm!!!
  mutate(growth = growth/10)
```

@@

```{r, eval = run_scbi & run_bw}
# Both Big Woods & SCBI
growth_df <- bind_rows(
  bw_growth_df %>% select(growth) %>% mutate(site = "bw"),
  scbi_growth_df %>% select(growth) %>% mutate(site = "scbi")
)
ggplot(growth_df, aes(x = growth, y = ..density.., fill = site)) +
  geom_histogram(alpha = 0.5, position = "identity", binwidth = 0.05) +
  labs(x = "Average annual growth in dbh (cm per yr)") +
  coord_cartesian(xlim = c(-0.5, 1))
```

@@

# Buffer polygon
square_buffer <- square_boundary %>% 
  st_buffer(dist = -0.1)

ggplot() +
  geom_sf(data = square_boundary) +
  geom_sf(data = square_buffer, col="red") 
```

@@

```{r, eval = run_scbi}
# SCBI
# Study region boundary polygon
scbi_boundary <- tibble(x = c(0,400,400,0,0), y = c(0,0,640,640,0)) %>% 
  sf_polygon()

# Buffer polygon
scbi_buffer <- scbi_boundary %>%
  st_buffer(dist = -max_dist)

# Convert data frame to sf object
scbi_growth_df <- scbi_growth_df %>% 
  st_as_sf(coords = c("gx", "gy"))

# ID which points are in buffer and which are not
buffer_index <- !st_intersects(scbi_growth_df, scbi_buffer, sparse = FALSE)
scbi_growth_df <- scbi_growth_df %>% 
  mutate(buffer = as.vector(buffer_index))

# Plot
ggplot() +
  geom_sf(data = scbi_boundary) +
  geom_sf(data = scbi_buffer, col="red") +
  # Only random sample of 1000 trees:
  geom_sf(data = scbi_growth_df %>% sample_n(1000), aes(col=buffer), size = 0.5)
```

>>>>

```{r}
library(tidyverse)
library(forestecology)
library(snakecase)
library(skimr)
library(sf)
library(sfheaders)
# devtools::install_github("rvalavi/blockCV")
library(blockCV)
library(tictoc)
library(yardstick)
library(viridis)
library(lubridate)

@@

```{r, eval = run_scbi}
# SCBI
scbi_2013 <- 
  "https://github.com/SCBI-ForestGEO/SCBI-ForestGEO-Data/raw/master/tree_main_census/data/census-csv-files/scbi.stem2.csv" %>% 
  read_csv() %>% 
  select(
    treeID, stemID, sp, quadrat, gx, gy, dbh, 
    date = ExactDate, codes, status
  ) %>%
  mutate(date = mdy(date))

scbi_2018 <-
  "https://github.com/SCBI-ForestGEO/SCBI-ForestGEO-Data/raw/master/tree_main_census/data/census-csv-files/scbi.stem3.csv" %>% 
  read_csv() %>% 
  select(
    treeID, stemID, sp, quadrat, gx, gy, dbh, 
    date = ExactDate, codes, status
  ) %>% 
  mutate(dbh = as.numeric(dbh),
         date = mdy(date)) 
```

@@

bw_growth_df <-
  # Merge both censuses and compute growth:
  compute_growth(bw_census_2008, bw_census_2014, id) %>%
  mutate(sp = to_any_case(sp)) %>%
  # Convert data frame to sf object DA note: should compute_growth do this??
  st_as_sf(coords = c("gx", "gy")) %>%
  # drop stemID
  select(-stemID)

@@

scbi_growth_df <- 
  # Merge both censuses and compute growth:
  compute_growth(census_df1, census_df2, id) %>%
  # they are mesuaring in mm while we are measuring in cm!!!
  mutate(growth = growth/10) %>%
  st_as_sf(coords = c("gx", "gy"))

@@

```{r, eval = run_scbi & run_bw}
# Both Big Woods & SCBI
growth_df <- bind_rows(
  bw_growth_df %>% st_drop_geometry %>% select(growth) %>% mutate(site = "bw"),
  scbi_growth_df %>% st_drop_geometry %>% select(growth) %>% mutate(site = "scbi")
)
ggplot(growth_df, aes(x = growth, y = ..density.., fill = site)) +
  geom_histogram(alpha = 0.5, position = "identity", binwidth = 0.05) +
  labs(x = "Average annual growth in dbh (cm per yr)") +
  coord_cartesian(xlim = c(-0.5, 1))
```

@@

# "Trees" in polygon
trees_df <- tibble(
    x = runif(100),
    y = runif(100)
  ) %>%
  sf_point()

# Buffer polygon
trees_df <- trees_df %>%
  add_buffer_variable(direction = "in", size = 0.1, region = square_boundary)

ggplot() +
  geom_sf(data = trees_df, aes(col = buffer))

@@

```{r, eval = run_scbi}
# SCBI
# Study region boundary polygon
scbi_study_region <- tibble(x = c(0,400,400,0,0), y = c(0,0,640,640,0)) %>% 
  sf_polygon()

# Add buffer variable to data frame
scbi_growth_df <- scbi_growth_df %>%
  add_buffer_variable(direction = "in", size = max_dist, region = scbi_study_region)

ggplot() +
  geom_sf(data = scbi_growth_df, aes(col = buffer))
```
